A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-10-19 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
[WIP] Finalization of CWP version for CSBS journal (#104)
* Use one column for author list

* CWP: appendices as a separate file, one column in cwp-csbs

* Fix a non itemized entry in the glossary (Concurrency Forum)

\begin{itemize}
\item
  to achieve improvements in software efficiency, scalability and
  performance, and to make use of advances in CPU, storage and network
  technologies in order to cope with the challenges ahead;
\item
  to enable new approaches to computing and software that can radically
  extend the physics reach of the detectors;
\item
  to ensure the long-term sustainability of the software through the
  lifetime of the HL- LHC;
\item
  to ensure data and knowledge preservation beyond the lifetime of
  individual experiments;
\item
  to attract the required new expertise by offering appropriate career
  recognition to physicists specialising in software development, and by
  an effective training effort to target all contributors in the
  community.
\end{itemize}

>>>>

\begin{itemize}
\item
  to achieve improvements in software efficiency, scalability and
  performance, and to make use of advances in CPU, storage and network
  technologies in order to cope with the challenges ahead;
\item
  to enable new approaches to computing and software that can radically
  extend the physics reach of the detectors;
\item
  to ensure the long-term sustainability of the software through the
  lifetime of the HL- LHC;
\item
  to ensure data and knowledge preservation beyond the lifetime of
  individual experiments;
\item
  to attract the required new expertise by offering appropriate career
  recognition to physicists specialising in software development and by
  an effective training effort to target all software contributors in the
  community.
\end{itemize}
